\documentclass[11pt]{letter}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\usepackage[T1]{fontenc}
\usepackage{xcolor}
\setlength{\longindentation}{0pt}
\signature{Haitham A. El-Ghareeb}
\address{Information Systems Department\\Faculty of Computers and Information Sciences\\Mansoura University, Mansoura, Egypt\\helghareeb@mans.edu.eg}
\begin{document}
\begin{letter}{Dr Devipriya Arumugam, Assistant Editor\\\textit{Scientific Reports}}
\opening{Dear Dr Arumugam,}

Thank you for handling our manuscript, ``A decentralized neutrosophic decision layer for global-state
freshness in microservices architectures'' (Submission ID c5ae1f20-9e89-4562-b69d-5dade5aca9d7), and
for the guidance on the Data Availability declaration. We have made the requested change and respond
point by point below. No scientific content was altered.

\textbf{Editor comment.} The Data Availability statement must comply with the journal's policy (the
phrasing ``available from the corresponding author on reasonable request'' and release ``upon
acceptance'' is not acceptable), and the Data Availability declaration in the submission system must
be set accordingly and match the manuscript.

\textbf{Author response.} We have revised the Data Availability (and, for consistency, the Code
Availability) statement to remove ``on reasonable request'' and the deferral to acceptance:

\begin{itemize}
\item The aggregated result summaries that underlie every figure and table are now provided with the
article as \textbf{Supplementary Information} (file \texttt{Supplementary\_Data\_1.zip}), so the data
behind every figure are available to the editors and reviewers through the submission system and are
published with the article.
\item The complete raw per-trial outputs and the full implementation are archived together in a
\textbf{Zenodo} record with a citable DOI, \textbf{10.5281/zenodo.20932989}. To protect ongoing work
the record is under restricted access during peer review; the editors and reviewers can access it
\emph{immediately} through the private link below, and the record will be released openly upon
publication (data under CC BY 4.0, code under the MIT licence).
\item We have set the Data Availability declaration in the submission system to \textbf{``Yes''} and
entered there the statement identical to the one now in the manuscript.
\end{itemize}

\textbf{Reviewer / editor access link (restricted Zenodo record):}\\
{\color{red}\textit{[Paste the Zenodo private/secret link here before uploading.]}}

\medskip
\textbf{Revised Data Availability statement (identical in the manuscript and the submission system):}

\begingroup\small\itshape
The aggregated result summaries underlying every figure and table in this article---the
per-configuration outcome summaries, the pairwise statistical comparisons, and the multi-seed
replication checks---are provided with this article as Supplementary Information. All results are
generated by the evaluation simulator under a fixed, content-hashed calibration and the recorded
random seeds described in the Methods; together with the figure and table generators they regenerate
every reported number. The complete raw per-trial outputs, together with the implementation, are
archived in a single Zenodo record (DOI: 10.5281/zenodo.20932989). During peer review this record is
held under restricted access to protect ongoing work; editors and reviewers are granted immediate
access through a private repository link provided to the editorial office, and it will be released
openly upon publication (data under the Creative Commons Attribution 4.0 International licence, code
under the MIT licence).
\endgroup

\medskip
We believe this fully addresses the comment. Thank you again for your time.

\closing{Sincerely,}
\end{letter}
\end{document}
